%!TEX root = ../dissertation.tex

\chapter{Methodology}
\label{chp:methodology}
This chapter outlines the methodology employed in the development and implementation of the Social Media Kit (SMKIT) project. It provides a comprehensive explanation of the approaches, tools, and techniques used to design, build, and test the system. The chapter begins with an overview of the research approach and system architecture, followed by detailed discussions on data collection, processing, and the integration of various components.
This chapter sets the foundation for understanding the practical implementation of SMKIT, which will be further detailed in the subsequent chapters.

\section{Introduction}
\label{sec:introduction}
This section introduces the methodology used for developing SMKIT. It outlines the approaches, techniques, and tools that will be detailed throughout the chapter.

\section{Research Approach}
\label{sec:research_approach}
This section provides a detailed explanation of the overall approach taken in the project.

\subsection{Qualitative vs. Quantitative Approach}
\label{subsec:qualitative_vs_quantitative}
Explain whether your methodology is based on qualitative or quantitative methods, and justify why that approach was chosen.

\subsection{Exploratory or Descriptive Research}
\label{subsec:exploratory_or_descriptive}
Discuss whether the research is exploratory, descriptive, experimental, or a mix, and explain the reasoning behind it.

\section{System Design and Architecture}
\label{sec:system_design_architecture}
This section explains the design decisions made for SMKIT, including the system architecture, components, and how they interact.

\subsection{System Architecture Overview}
\label{subsec:system_architecture_overview}
Provide a high-level overview of the system architecture, including diagrams that illustrate how different components of SMKIT interact.

\subsection{Technological Stack}
\label{subsec:technological_stack}
Describe the technologies and tools used to implement SMKIT, including any frameworks or programming languages like Python, Flask, or others.

\subsection{Module Development for Negapedia Integration}
\label{subsec:module_development_negapedia}
Explain the development of the specific module created to integrate data from Negapedia, highlighting any key challenges or innovations.

\section{Data Collection and Preparation}
\label{sec:data_collection_preparation}
This section describes how data is gathered, processed, and prepared for use in the SMKIT system.

\subsection{Web Scraping Tools and Techniques}
\label{subsec:web_scraping_tools_techniques}
Discuss the web scraping tools and techniques employed, such as BeautifulSoup or Scrapy, and how they were used to extract data from web pages.

\subsection{Data Cleaning}
\label{subsec:data_cleaning}
Explain the methods used to clean and process the raw data, including handling missing values, removing duplicates, and correcting errors.

\subsection{Data Transformation}
\label{subsec:data_transformation}
Describe the process of transforming raw data into a usable format for the system, such as converting text into structured data or normalizing values.

\section{Implementation}
\label{sec:implementation}
This section details the implementation of SMKIT, including the development of key modules and the integration of components.

\subsection{Module for Content Automation}
\label{subsec:module_for_content_automation}
Explain how the module for content automation was developed, including the algorithms or logic used to generate posts or content for social media platforms.

\subsection{Integration with Negapedia}
\label{subsec:integration_with_negapedia}
Describe how Negapedia’s data is integrated into the SMKIT system, focusing on the specific integration methods or APIs used.

\subsection{Social Media Platform Integration}
\label{subsec:social_media_integration}
Discuss the methods used to integrate SMKIT with social media platforms (e.g., Twitter, Facebook, Instagram) for automatic content sharing.

\section{Challenges and Limitations}
\label{sec:challenges_limitations}
This section discusses any technical, logistical, or methodological challenges encountered during the project, as well as the limitations of SMKIT.

\subsection{Technical Challenges}
\label{subsec:technical_challenges}
Describe the technical difficulties faced during development, such as integrating with social media APIs or dealing with large-scale data extraction.

\subsection{Limitations of SMKIT}
\label{subsec:limitations_of_smkit}
Explain the limitations of the SMKIT system, including any features or capabilities that are yet to be implemented or limitations in performance.

\section{Conclusion}
\label{sec:methodology_conclusion}
Summarize the key points of the methodology, reflect on the approach taken, and provide a brief transition to the next chapter, which will focus on the **Implementation** or **Results** of SMKIT.
